% XeLaTeX can use any Mac OS X font. See the setromanfont command below.
% Input to XeLaTeX is full Unicode, so Unicode characters can be typed directly into the source.

% The next lines tell TeXShop to typeset with xelatex, and to open and save the source with Unicode encoding.

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}

% Will Robertson's fontspec.sty can be used to simplify font choices.
% To experiment, open /Applications/Font Book to examine the fonts provided on Mac OS X,
% and change "Hoefler Text" to any of these choices.

\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Mapping=tex-text]{Times}
\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Gill Sans}
\setmonofont[Scale=MatchLowercase]{Andale Mono}

\title{University of Glasgow Software Team Project}
\author{Team 12 Organisational Document}
\date{\today}                                           

\begin{document}
\maketitle
\subsection*{Team Members}
Paul McHard

Nicholas Ferrera

Lewis Renfrew

Kayleigh Chisholm

Eoghan Malone
\subsection*{Roles and Responsibilities}
Programming tasks:
\begin{enumerate}
\item Core functionality - Lewis and Paul
\item Extension to full functionality [Production Coding] - Eoghan and Nicholas
\item Database Development - Paul and Eoghan
\item Command Line Interface - Kayleigh and Nicholas
\item Web Interface  - Lewis and Nicholas
\end{enumerate}
Other Tasks:
\begin{enumerate}
\item Systems Analysis and Design - Kayleigh and Paul
\item Code Readability and Structuring - Lewis and Eoghan
\item Documentation - Paul, Kayleigh and Eoghan
\item Testing - all team
\end{enumerate}

Scrum Manager will be Eoghan Malone, responsible for organising sprints.

Git Librarian will be Nicholas Ferrera, responsible for managing the github repository and encouraging regular commits by all team members.


\subsection*{Authority}
Project Manager will be Paul McHard. Decisions will be largely be made on group consensus, the project manager will have organisational responsibility and make decisions where need be.
\subsection*{Communication}
Team will meet twice a week on Tuesdays and Thursdays to discuss progress. Team met on Wednesday and Friday in week 1 to establish roles, responsibilities and workload distribution. 

Team also makes use of an email chain and instant messaging group chat for rapid communication. 

\subsection*{Information Management}
Code will be organised and stored centrally using Git, with a Github repository hosted by the Git Librarian.
All other documentation will be shared and stored using Google Drive.
\subsection*{Tools}
The following tools will be implemented:
\begin{itemize}
\item Eclipse
\item Github
\item Google Drive
\item DB workbench
\end{itemize}
\end{document}  