\documentclass[12pt, oneside]{article}   	
\usepackage[a4paper,margin=1in]{geometry}                		            		
\usepackage[parfill]{parskip}    	
\usepackage{graphicx}				
\usepackage{amssymb}
\usepackage{fontspec}
				
\begin{document}

\subsection*{One Page Review}
\subsection*{Identification of concerns}
The authors should start by clearly laying out the aims of the report, the proper context and topics they will discuss to address their aims in their introduction. Discussion of prevalence of cloud security risks is good and well researched, however this is dwelt on too heavily. The context of the client is mentioned passingly and not properly detailed. The authors did well to adhere to the specified structure and breakdown of page limitation. The use of risk assessment criteria in appendix I. was done well.

The authors need to draw proper conclusions to each of the respective point they address throughout the section. In particular in the case of data storage, the topic has clearly been well researched and the authors should continue to work in this style, however, discussion of the issue is continued on longer than necessary, losing focus of the point and failing to converge to a clear identification of risk posed. This issue occurs throughout the section but is most observable in discussion of data storage. The authors should review and streamline their discussions, and make sure to properly identify the respective risks posed. This is done well in collusion concern section and to an extent in extensibility and accessibility discussion.

The authors need to address the specific question that has been asked: concern over use of employees using personal clouds for storage of business data. On multiple occasions throughout the document the authors seem to discuss the risks of the client directly being hacked or the clients use of cloud storage as a company. The context of the question asked needs to be clearly indicated throughout both sections.
\subsection*{Assessment of concerns}
The two main issues that were identified already of need for convergence to a point and need for focus on context of the question asked are heightened in this section. The authors continue to discuss their research findings and largely do not draw back to the risks they identified nor attempt to make an assessment. The exception is their section on collusion concerns, which is clear and concise in its assessment of the same risks it identified previously. The authors have clearly researched each topic thoroughly, and should continue to involve as much of their research as is relevant, but there is an over-reliance on discussing researched topics without compounding it with an over arching risk assessment. 

The authors again infer in multiple places, particularly data storage and accessibility, that Mostel & Wilder are acting as a cloud customer as a corporation, and fail to address again the question of employees using personal clouds. This is not seen throughout but is notable enough that it corrupts the readers view on what the authors aim to achieve with the report. 
\subsection*{Policy}

\end{document} 